Enhancement of SDR in Thessaloniki

### 2024-05-01 GHI_enh_Aeronet.tex
Commit 2024-05-01 17:11

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-04-26}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}
Cross over point: 2014.75 
\end{verbatim}

@@

SZA min : 0.00133216113167738

SZA mean : 0.00192971268218197

SZA median : 0.00178690927379885

@@

@@

@@

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-05-01}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}
Cross over point: 2005 
\end{verbatim}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-4} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-5} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-6} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-7} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-8} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-9} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-10} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-11} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-12} \end{center}

SZA min : 0.00137165912186399

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-13} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-14} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-15} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-16} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-17} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-18} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-19} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-20} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-21} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-22} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-23} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-24} \end{center}

SZA mean : 0.0020024477410843

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-25} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-26} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-27} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-28} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-29} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-30} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-31} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-32} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-33} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-34} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-35} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-36} \end{center}

SZA median : 0.00184853525463023

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1579}}
  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1184}}
  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1053}}
  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1316}}
  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1711}}
  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1579}}
  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1579}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
Intercept
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Slope
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Month
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
MeanGlo
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Type
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Zeropoint
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
SlopeRela
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
-1102 & 0.8309 & 1 & 565.8 & SZA min & 2014 & 0.001469 \\
-810.5 & 0.7648 & 2 & 721.8 & SZA min & 2015 & 0.00106 \\
-6892 & 3.872 & 3 & 888.2 & SZA min & 2015 & 0.00436 \\
-1277 & 1.124 & 4 & 974.5 & SZA min & 2015 & 0.001153 \\
-982.7 & 0.9904 & 5 & 1004 & SZA min & 2015 & 0.0009866 \\
375.1 & 0.3116 & 6 & 993.2 & SZA min & 2015 & 0.0003138 \\
-140.7 & 0.5624 & 7 & 984 & SZA min & 2015 & 0.0005715 \\
444.2 & 0.2576 & 8 & 967.6 & SZA min & 2015 & 0.0002663 \\
-3.347 & 0.4436 & 9 & 872.7 & SZA min & 2015 & 0.0005082 \\
-1081 & 0.9159 & 10 & 758.3 & SZA min & 2015 & 0.001208 \\
-2109 & 1.345 & 11 & 565.3 & SZA min & 2015 & 0.002379 \\
-1598 & 1.044 & 12 & 477.6 & SZA min & 2014 & 0.002186 \\
-1221 & 0.756 & 1 & 293.9 & SZA mean & 2014 & 0.002573 \\
-1063 & 0.7194 & 2 & 377.8 & SZA mean & 2015 & 0.001904 \\
-1776 & 1.125 & 3 & 485.6 & SZA mean & 2015 & 0.002317 \\
-1680 & 1.118 & 4 & 561.4 & SZA mean & 2015 & 0.001992 \\
-1628 & 1.111 & 5 & 599.9 & SZA mean & 2015 & 0.001852 \\
-262.2 & 0.4374 & 6 & 606.9 & SZA mean & 2015 & 0.0007207 \\
-745.5 & 0.6689 & 7 & 592.1 & SZA mean & 2015 & 0.00113 \\
-122.7 & 0.3402 & 8 & 566.4 & SZA mean & 2015 & 0.0006007 \\
-474.5 & 0.4816 & 9 & 477.8 & SZA mean & 2015 & 0.001008 \\
-1443 & 0.9151 & 10 & 394.4 & SZA mean & 2015 & 0.00232 \\
-2438 & 1.364 & 11 & 277.9 & SZA mean & 2015 & 0.004907 \\
-1179 & 0.7187 & 12 & 265.7 & SZA mean & 2014 & 0.002705 \\
-1216 & 0.772 & 1 & 331.6 & SZA median & 2014 & 0.002328 \\
-1041 & 0.7293 & 2 & 419.7 & SZA median & 2015 & 0.001738 \\
-1743 & 1.129 & 3 & 527.8 & SZA median & 2015 & 0.00214 \\
-1654 & 1.123 & 4 & 595.7 & SZA median & 2015 & 0.001884 \\
-1595 & 1.105 & 5 & 620.6 & SZA median & 2015 & 0.00178 \\
-243.2 & 0.4343 & 6 & 619.6 & SZA median & 2015 & 0.0007009 \\
-708.1 & 0.6584 & 7 & 608.4 & SZA median & 2015 & 0.001082 \\
-109.2 & 0.3477 & 8 & 595.2 & SZA median & 2015 & 0.0005842 \\
-441.5 & 0.4846 & 9 & 516.9 & SZA median & 2015 & 0.0009376 \\
-1433 & 0.9306 & 10 & 435.1 & SZA median & 2015 & 0.002139 \\
-2464 & 1.395 & 11 & 314.5 & SZA median & 2015 & 0.004436 \\
-1176 & 0.7354 & 12 & 302.4 & SZA median & 2014 & 0.002432 \\
\end{longtable}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-37} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-38} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-39} \end{center}
